Machine Learning based TIR predictor

### 2020-05-14 main.tex
Draft for GPUCB description.
Updated Results (Initial Bandit Design) 140520

\subsection{Initial bandit recommended designs}
As mentioned previously, for the first round of bandit-guided designs we used data-set available from \textcite{jervis2018machine}. This set contains 113 non-repeated records for 56 unique RBS sequences with the respective TIR label. The label values are between 0 - 100,000 and skewed, which is shown in Figure xx. We have normalised the label to 0 - 1 using the min-max normalisation.

>>>>

\subsection{Initial bandit recommended designs}
As mentioned previously, for the first round of bandit-guided designs we used data-set available from \textcite{jervis2018machine}. This set contains 113 non-repeated records for 56 unique RBS sequences with the respective TIR label. The label values are between 0 - 100,000 and skewed, which is shown in Figure xx. \\
First, we have normalised the label to 0 - 1 using the min-max normalisation. Next, we have \textcolor{red}{transformed (not sure what would be the best term here} the sequences with the sum of kernels as described previously. Finally, Gaussian Process was used to process the data and allow us to recommend 60 RBS sequences.
